MCC Kids Model Predictions

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
cache rsa and replace maps with foreach

var pragmaticListener = function(utterance, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

var speaker = function(obj, lexiconName, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
}

var literalListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
}

@@

@@

>>>>

var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
})

var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
})

var literalListener = cache(function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
})

@@

var foreach = function(fn, lst) {
    var foreach_ = function(i) {
        if (i < lst.length) {
            fn(lst[i]);
            foreach_(i + 1);
        }
    };
    foreach_(0);
};

@@

  foreach(function(row){
